Verifying Demonstrations

### 2017-07-20 properties.tex
Adds comments on partial order for authenticity

    \item A\ref{SpatiallyRelated} is provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} together bind the data to the time of 
the event whereas \cref{SpatiallyRelated} binds the data spatially to the 
event.

One primitive that provides the properties 
\cref{CreatedAfterStart,CreatedBeforeEnd} is a block chain with a distributed 
consensus protocol.

\begin{frame}
  \begin{question}
    Are there other strucutres than block chains?
    E.g.~\cite{BlockchainFreeCryptocurrencies}.
  \end{question}
\end{frame}

>>>>

    \item A\ref{SpatiallyRelated} is provided by \iacf{LP}.
  \end{itemize}
\end{idea}
}
\end{frame}
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{strict partial 
  order}\footnote{%
  A relation \(<\) which is irreflexive, antisymmetric and transitive.
}.
If some objects in the set relate to known points in time, then the partial 
order allows to relate the data to the time of the event.
\Cref{SpatiallyRelated} binds the data spatially to the event.

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a block 
chain.

\begin{frame}
  \begin{question}
    Are there other structures than block chains?
    E.g.~\cite{BlockchainFreeCryptocurrencies}.
  \end{question}
\end{frame}
